---
title: "Homework11"
author: "Rachel Swanwick"
date: "4/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Home Page](index.html)

```{r}
# Question #1: Repeat the exercise from the Batch Processing Lecture (5 April), but do it using real data sets rather than purely simulated. Check with folks in your lab to see if there are multiple data sets available for analysis, or ask Nick, Lauren, or Emily for suggestions for other data sources. Stick to simple data analyses and graphics, but try to set it up as a batch process that will work on multiple files and save summary results to a common file.

# -------------------------------
# FUNCTION batch_processing 
# description: using simulated data from class to make batch processing 
# inputs: file_n = number of files to create
#       file_folder = name of folder for random files
#       file_size = c(min,max) number of rows in file
#       file_na = number on average of NA values per column
# outputs: set of random files
##################################
batch_processing  <- function(file_n=10,
                        file_folder="BatchFiles/",
                        file_size=c(15,100),
                        file_na=3){
for (i in seq_len(file_n)) {
file_length <- sample(file_size[1]:file_size[2],size=1) # get number of rows
var_x <- runif(file_length) # create random x
var_y <- runif(file_length) # create randon y
df <- data.frame(var_x,var_y) # bind into a data frame
bad_vals <- rpois(n=1,lambda=file_na) # determine NA number
df[sample(nrow(df),size=bad_vals),1] <- NA # random NA in var_x
df[sample(nrow(df),size=bad_vals),2] <- NA # random NA in var_y

# create label for file name with padded zeroes
file_label <- paste(file_folder,
                       "ranFile",
                       formatC(i,
                       width=3,
                       format="d",
                       flag="0"),
                       ".csv",sep="")

# set up data file and incorporate time stamp and minimal metadata
write.table(cat("# Simulated random data file for batch processing","\n",
                    "# timestamp: ",as.character(Sys.time()),"\n",
                    "# RHS","\n",
                    "# ------------------------", "\n",
                    "\n",
                    file=file_label,
                    row.names="",
                    col.names="",
                    sep=""))

# now add the data frame
write.table(x=df,
            file=file_label,
            sep=",",
            row.names=FALSE,
            append=TRUE)


}
} # end of batch processing function_name)

batch_processing()
#---------------------------------
```

```{r}
##################################
# Global variables
file_folder <- "BatchFiles/"
n_files <- 100
file_out <- "StatsSummary.csv"
data_list <- list()
#######################################
# Create 100 random data sets
dir.create(file_folder)
batch_processing(file_n=n_files)
file_names <- list.files(path=file_folder)

# Create data frame to hold filenames 
ID <- seq_along(file_names)
file_name <- file_names

stats_out <- data.frame(ID,file_name)

# batch process by looping through individual files
for (i in seq_along(file_names)) {
  data_list[[i]] <- read.table(file=paste(file_folder,file_names[i],sep=""),
                     sep=",",
                     header=TRUE)

}

# Using lapply with the list to find the sum of each of its elements 
lapply(data_list, sum, na.rm=TRUE)